The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-02-17 analysis/paper/paper.qmd
Update text
Start methods section on topic modeling
Add topicmodels package

## Text processing and analysis
library(tidytext)
library(SnowballC)
library(tm)

@@

A total number of `r nrow(emu_theses)` were analysed.

@@

>>>>

## Text processing and analysis
library(tidytext)
library(SnowballC)
library(tm)
library(topicmodels)

@@

A total number of `r nrow(emu_theses)` out of `r nrow(theses_all)` were analysed.

@@

## Topic model

Similar to topic clustering on numeric data, topic modeling is a method of unsupervised classification of topics found in a group of documents [@silge2017].
